q1)Write a program to create a vector containing 10 elements, 
then copy the contents of the original vector into a new 
vector using loops
```{r}
vec=c(5:10,1:4)
vec2=c()
for(i in 1:length(vec))
{
  vec2[i]=vec[i]
}
vec2
```

q2)A program to find the sum of numbers between the range 
which is specified by the user. This has to be done using 
functions and functions must return the sum.  
```{r}
func=function(a,b)
{
  len=b-a
  sum1=a
  for(i in 1:len)
  {
    sum1=sum1+i
  }
  sum1
}

func(10,30)
```
q3)In the USArrests data set, find out the top 3 states which
has the highest assault 
```{r}
tt<-data.frame(USArrests)
tt<-tt[order(tt$Assault,decreasing = TRUE),]
tt[1:3,][0]

n<-data.frame(USArrests)
n<-n[order(n$Murder,decreasing = TRUE),]
n[1,][0]
```

q4)A program to create a new data frame which contains all 
the data from USArrests, except that instead of the names of 
the states, they should be replaced by numbers starting from 
1 
```{r}
df1<-data.frame(USArrests)
rownames(df1)<-c(1:nrow(df1))
#rownames(df1)<-c(1:50)
df1

#or
j=1
new_df=data.frame()
  for(j in 1:ncol(USArrests))
  {
    for(i in 1:nrow(USArrests))
    {
      new_df[i,j]=USArrests[i,j]
    }
  }
new_df

```


